---
title: "Rendering a Single Chapter of your Thesis"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = NA)
```

As part of writing a thesis it is expected that individual chapters will need to be produced without the entire thesis being put together. These would normally be passed to a student's supervisor(s) for comment. 

With that in mind the `single_chapter` function allows this to happen. It creates a temporary R Markdown file (that is deleted after the pdf is created) with a YAML header that includes the bibliography file provided and inserts the R Markdown file of the chosen chapter as a "child" document. For more information on child documents please see the [knitr](https://yihui.name/knitr/demo/child/) documentation. 

To use the function you can copy and paste the following line into the console 

```{r, eval = FALSE}
single_chapter("01-chap1.Rmd")
```

or ff you are using RStudio there is also an addin which allows the R Markdown file to be chosen interactively.  

To find references the function will parse the contents of `index.Rmd`, find the line that starts `bibliography` and add that line to the temporary document. This means that `index.Rmd` **needs** to be in the current working directory.
